### 2016-10-12 methodsPaper/tex/abstract.tex

>>>>

Comparative risk assessment exercises to quantify the health potential of active transportation have been performed in the United States on a limited basis. Current methodologies, which rely on entensive data collection activities and user expertise, have estimated health benefits for select metropolitan areas under a few alternative scenarios. These analyses have largely been conducted using the Intergrated Transport Health Impacts Model (IHTIM), which was developed in the UK and has been adapted for use in the US, primarility California. Here we present an implementation of one portion of ITHIM's comparative risk assessment framework to model the health impacts of modified physical activity patterns from biking and walking. Using the newly-developed ITHIM package available for the R Software platform publically-available datasets with coverage for the entire US are used to quantify changes in diability adjusted life years. We examine the sensitivity of outcomes for the nation to input parameters; active travel time, non-travel physical activity time, specifically. The revised R package implemention of ITHIM's physical activity component provides a robust and stable means of examining the potential for changes in transportation behavior in the US, and the distribution of those benefits across age and gender categories.
